\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    firstname=Adrian,
    %middleinitial=,
    lastname=Beer,
    email=adrianbeerka@gmail.com,
    phone=+49 1575 6642668,
    %linkedin=johndoe,
    %github=adrianbeer,
    city=Kiel,
    state=Germany
]

\vspace{0.25in}
\today
\vspace{0.15in}


Greetings,
My name is Adrian Beer and I would like to apply for a position as an entry-level quantitative strategist at WorldQuant. 
I'm currently writing my Master's Thesis at the University of Kiel in Quantitative Finance and I'm interested in working at WorldQuant afterwards (around/after July). 
My background is in computer science which I studied at the KIT in Karlsruhe. 
There I started to develop and pursue my interest in data science and systematic trading strategies. 
I'm passionate about statistics, math and software developement and I believe that the position at WorkQuant would suit my strenghts and interests, making it an ideal opportunity.

Throughout my computer science studies I've developed a strong background in data science and machine learning. 
I've also gained experience in developing large systems in Python within teams of up to 5 people. 
After developing my interest in finance I started to develop and backtest systematic trading strategies and my current Master's Thesis topic is the developement of a profitable news trading strategy using Large Language Models (LLMs). 
I've also accumulated valuable work experience as a data science working student at the Vattenfall Energy Trading GmbH, where I assisted a US power trader by performing time series analysis, and developing non-linear pricing models.
I'm looking for an environment in which I can learn, but also contribute and discuss ideas about various asset classes and algorithms with an enthusiastic team and most importantly: build a system that works.
I'd be delighted to convince you of my dedication and qualifications in a personal conversation.
Best Regards,
Adrian Beer


\vspace{.15in}

Adrian Beer

\end{document}